### 2016-08-26 ReviewComments/response.tex

\documentclass{vldb}
\usepackage{url}
\newcounter{ctResp}
\newcommand{\response}[1]{
\addtocounter{ctResp}{1}
\textbf{Response \arabic{ctResp}:} #1 \\}

\begin{document}
\title{Response to reviewers' comments for Paper \# 278}
\maketitle

We are grateful to all the reviewers for the generous and insightful
comments which help us to improve this work to a better level. Hereby, 
we summarize our responses and corresponding revisions.
We wish this feedback could help to clear reviewers' concerns 
in publishing this paper.

\input{review1}
\input{review2}
\input{review3}
\input{meta}

\end{document}

### 2016-08-26 sec1_introduction.tex
Revision
almost completed

A crucial task of data analysis on top of trajectories is 
to discover co-moving objects. A \emph{co-movement} pattern~\cite{li2013managing,zheng2015survey} 
refers to a group of objects traveling together for a certain period of time 
and the group is normally determined by their spatial proximity. 
A pattern is prominent if the size of the group exceeds $M$ and the length of the duration exceeds $K$, where $M$ and $K$ are parameters specified by users. Rooted from such a basic definition 
and driven by different mining applications, there are a bunch of variants 
of co-movement patterns that have been developed with more advanced constraints.

@@

Therefore, our primary contributions in this paper are to close these two gaps. 
First, we propose the \emph{general co-movement pattern} (GCMP) which models
various co-moment patterns in a unified way and can avoid 
the \emph{loose-connection} anomaly. In GCMP, we introduce a new gap parameter $G$ to pose a constraint on the temporal gap between two consecutive segments. By setting a feasible $G$, the loose-connection anomaly can be effectively controlled. In addition, our GCMP is both general and expressive. It can be reduced to any of the previous patterns by customizing its parameters.

>>>>

A crucial task of data analysis on top of trajectories is 
to discover co-moving objects. A \emph{co-movement} pattern~\cite{li2013managing,zheng2015survey} 
refers to a group of objects traveling together for a certain period of time 
and the group is normally determined by their spatial proximity. 
A pattern is prominent if the size of the group exceeds $M$ and the length of the duration exceeds $K$, where $M$ and $K$ are parameters specified by users. Rooted from such a basic definition 
and driven by different mining applications, there are \revised{many} variants 
of co-movement patterns that have been developed with more advanced constraints.

@@

Therefore, our primary contributions in this paper are to close these two gaps. 
First, we propose the \emph{general co-movement pattern} (GCMP) which models
various co-moment patterns in a unified way and can avoid 
the \emph{loose-connection} anomaly. In GCMP, we introduce a new gap parameter $G$ to pose a constraint on the temporal gap between two consecutive segments. 
%\revised{In GCMP, we adopt the concept of \emph{gap parameter $G$}
%in sequential pattern mining field~\cite{srikant1996mining} to constrain the temporal distance between two consecutive %segments.} 
By setting a feasible $G$, the loose-connection anomaly can be effectively controlled. In addition, our GCMP is both general and expressive. It can be reduced to any of the previous patterns by customizing its parameters.

### 2016-08-26 sec5_spm.tex
Revision
almost completed

We use \emph{star} as the data structure to capture the pair relationships. 
To avoid duplication, as $G_t$ is an undirected graph and an edge may appear in multiple stars, 
we enforce a global vertex ordering among the objects and propose a concept named \textit{directed star}.

@@

\subsection{Apriori Enumerator}
Intuitively, given a GCMP with an object set $\{o_1,o_2,\ldots,o_m\}$, 
all the pairs of $\langle o_i,o_j \rangle$ with $1\leq i<j\leq m$ must 
be connected in the associated temporal graphs $\{G_t\}$. This inspires us to leverage the classic Apriori algorithm to enumerate all the valid GCMPs starting from pairs of objects. However, we observe that the monotonicity property does not hold between an object set and its supersets.

@@

Theorem~\ref{LEM:SPM_CORRECT} implies that no mining efforts are wasted in discovering redundant patterns  
%that no replication is required 
in the SPARE framework, which is superior to the TRPM baseline. Finally, we show the correctness of the SPARE framework.
\begin{theorem}
\label{THM:SPM_CORRECT}
The SPARE framework guarantees completeness and soundness.
\end{theorem}
\begin{proof}
See Appendix~\ref{apx:spm_correct}.
\end{proof}

>>>>

We use \emph{star}~\cite{yoo2006joinless} as the data structure to capture the pair relationships. 
To avoid duplication, as $G_t$ is an undirected graph and an edge may appear in multiple stars, 
we enforce a global vertex ordering among the objects and propose a concept named \textit{directed star}.

@@

\subsection{Apriori Enumerator}
Intuitively, given a GCMP with an object set $\{o_1,o_2,\ldots,o_m\}$, 
all the pairs of $\langle o_i,o_j \rangle$ with $1\leq i<j\leq m$ must 
be connected in the associated temporal graphs $\{G_t\}$. This inspires us to leverage the classic Apriori algorithm~\cite{agrawal1994fast} to enumerate all the valid GCMPs starting from pairs of objects. However, we observe that the monotonicity property does not hold between an object set and its supersets.

@@

Theorem~\ref{LEM:SPM_CORRECT} implies that no mining efforts are wasted in discovering redundant patterns  
%that no replication is required 
in the SPARE framework, which is superior to the TRPM baseline. Finally, we show the correctness of the SPARE framework.
\begin{theorem}
\label{THM:SPM_CORRECT}
The SPARE framework guarantees completeness and soundness.
\end{theorem}
\vspace{-5 mm}
\begin{proof}
See Appendix~\ref{apx:spm_correct}.
\end{proof}

### 2016-08-26 sec6_experiment.tex
Revision
almost completed

\textbf{Environment Setup}: We use Yarn\footnote{\url{http://hadoop.apache.org/docs/current/hadoop-yarn/hadoop-yarn-site/YARN.html}} to manage our cluster. We pick one machine as Yarn's master node, and for each of the remaining machines, we reserve one core and $2$GB memory for Yarn processes. We deploy our GCMP detector on Apache Spark 1.5.5~\cite{zaharia2012resilient} with the remaining $11$ nodes as the computing nodes.
To fully utilize the computing resources, we configure each node to run five executors, each taking three cores and $5$GB memory. In Spark, one of the $55$ executors is taken as the Application Master for coordination, therefore our setting results in $54$ executors.
All our implementations as well as cluster setups are open-sourced in Github\footnote{\url{https://github.com/fanqi1909/TrajectoryMining/}}.

@@

%\begin{figure}[h]
%\centering
%	\begin{subfigure}[b]{0.22\textwidth}
%	 \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_o.eps}
%        \caption{Shopping vary $O_r$}
%    \end{subfigure}
% 	 \begin{subfigure}[b]{0.22\textwidth}
%        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_o.eps}
%        \caption{Geolife vary $O_r$}
%    \end{subfigure}
%    	 \begin{subfigure}[b]{0.22\textwidth}
%        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_o.eps}
%        \caption{Taxi vary $O_r$}
%    \end{subfigure}
%    \begin{subfigure}[b]{0.22\textwidth}
%	 \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_t.eps}
%        \caption{Shopping vary $T_r$}
%    \end{subfigure}
% 	 \begin{subfigure}[b]{0.22\textwidth}
%        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_t.eps}
%        \caption{Geolife vary $T_r$}
%    \end{subfigure}
%    	 \begin{subfigure}[b]{0.22\textwidth}
%        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_t.eps}
%        \caption{Taxi vary $T_r$}
%    \end{subfigure}
% \caption{Scalability of SPARE and TRPM wrt. $O_r$ and $T_r$}
% \label{exp:performance_vary_OT}
%\end{figure}

@@

\begin{figure}[h]
\centering
	  \includegraphics[width=0.4\textwidth]{/exp/spare/detail.eps}
    \caption{Breakdown of cost of SPARE and SPARE-RD.}
    \label{exp:wl}
\end{figure}

\begin{table}[h]
\centering \small
\begin{tabular}{|l|c|c|c|c|}
\hline
\multirow{2}{*}{\textbf{Dataset}} & \multicolumn{2}{l|}{\textbf{SPARE-RD}} & \multicolumn{2}{l|}{\textbf{SPARE}} \\ \cline{2-5} 
                         & Straggler        & Std. Dev.     & Straggler       & Std. Dev.      \\ \hline
Shopping                 & 295              & 41         & 237             & 21       \\ \hline
GeoLife                  & 484              & 108        & 341             & 56       \\ \hline
Taxi                     & 681              & 147        & 580             & 96       \\ \hline
\end{tabular}
  \caption{Statistics of execution time (in seconds) among executors.}
  \label{tbl:strags}
\end{table}

\subsubsection{Load balance}
To study the effect of load balance in the SPARE framework, we use random task allocation (the default setting of Spark) as a baseline, denoted by SPARE-RD, and compare it with our best-fit method. In best-fit, the largest unassigned star is allocated to the currently most lightly loaded reducer.
Figure~\ref{exp:wl} (a) shows the breakdown of the costs in the map-reduce stages for SPARE and SPARE-RD. We observe that the map and shuffle time of SPARE and SPARE-RD are identical. The difference is that SPARE incurs an additional overhead to generate an allocation plan for load balance (around $4\%$ of the total cost), resulting in significant savings in the reduce stage (around $20\%$ of the total cost). We also report the cost of \emph{straggler}, i.e., the longest job, and the standard deviation (Std. Dev.) for all jobs in Table~\ref{tbl:strags}, whose results clearly verify the effectiveness of our allocation strategy for load balance.

\subsubsection{Scalability}
When examining SPARE with increasing computing resources (number of machines), we also compare SPARE with the state-of-the-art solutions for \emph{swarm} and \emph{platoon} in the single-node setting. Since the original \emph{swarm} and \emph{platoon} detectors cannot handle very large-scale datasets, we only use 60\% of each dataset for evaluation. To make fair comparisons, we customize two variants of SPARE to mine \emph{swarm}s and \emph{platoon}s, which are denoted as SPARE-S and SPARE-P respectively. The customization is according to the settings in Table~\ref{tbl:patterns} and the results are reported in Figure~\ref{exp:scalability}. 
First, the centralized schemes are not suitable to discover patterns in 
large-scale trajectory databases. It takes nearly $30$ hours to 
detect \emph{swarm}s and $11$ hours to detect \emph{platoon}s in the Taxi dataset in a single machine. 
In contrast, when utilizing the multi-core environment, 
SPARE-P achieves $7$ times speedup and SPARE-S achieves $10$ times speedup. 
%our TRPM and SPARE achieves 2.4 times and 7.1 times speedup respectively. 
Second, we see that SPARE schemes demonstrate promising scalability in terms of the number of machines available. The running times decrease almost inversely as more machines are used. 
When all the $11$ nodes ($162$ cores) are available, 
SPARE-P is upto $65$ times and SPARE-S is upto $112$ times better than the state-of-the-art centralized schemes.
%than \emph{platoon} and SPARE-S is upto $112$ times better than \emph{swarm}.
%state-of-the-art \emph{platoon} detector in a centralized server.

>>>>

\textbf{Environment Setup}: We use Yarn\footnote{\url{http://hadoop.apache.org/docs/current/hadoop-yarn/hadoop-yarn-site/YARN.html}} to manage our cluster. We pick one machine as Yarn's master node, and for each of the remaining machines, we reserve one core and $2$GB memory for Yarn processes. We deploy our GCMP detector on Apache Spark 1.5.2~\cite{zaharia2012resilient} with the remaining $11$ nodes as the computing nodes.
To fully utilize the computing resources, we configure each node to run five executors, each taking three cores and $5$GB memory. In Spark, one of the $55$ executors is taken as the Application Master for coordination, therefore our setting results in $54$ executors. \revised{We set the number of partitions to be $486$ to fully utilize the parallelism provided by the multi-threading of every core.}
All our implementations as well as cluster setups are open-sourced in Github\footnote{\url{https://github.com/fanqi1909/TrajectoryMining/}}.

@@

\revised{
\textbf{Resources}: Table~\ref{tbl:resource} lists the system resources taken by TRPM and SPARE under the default setting. Both TRPM and SPARE are resource efficient as they only occupy less than 20\% 
of the available memory which reveals their potential to handle larger trajectories. Again, SPARE outperforms TRPM in both execution time and memory usage which dues
to the set of effective pruning procedures.

\begin{table}[h]
\small
\begin{tabular}{|l|c|c|c|c|}
\hline
\multicolumn{1}{|c|}{\textbf{Dataset}} & \textbf{Method} & \textbf{Time} & \textbf{Vcore-seconds} & \textbf{Memory} \\ \hline
\multirow{2}{*}{Shopping}              & TRPM            & 597                               & 90,859                 & 10,019               \\ \cline{2-5} 
                                       & SPARE           & 334                               & 47,430                 & 8,613                \\ \hline
\multirow{2}{*}{Geolife}               & TRPM            & 747                               & 106,428                & 18,454               \\ \cline{2-5} 
                                       & SPARE           & 480                               & 49,835                 & 14,369               \\ \hline
\multirow{2}{*}{Taxi}                  & TRPM            & 3,648                             & 503,460                & 51,691               \\ \cline{2-5} 
                                       & SPARE           & 812                               & 89,390                 & 35,912               \\ \hline
\end{tabular}
\caption{Resources taken for TRPM and SPARE. Time is in seconds representing observed performance. Vcore-seconds is the aggregate of time spent in each core. Memory is in MB representing the actual size of RDDs.}
\label{tbl:resource}
\end{table}
}
%\begin{figure}[h]
%\centering
%	\begin{subfigure}[b]{0.22\textwidth}
%	 \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_o.eps}
%        \caption{Shopping vary $O_r$}
%    \end{subfigure}
% 	 \begin{subfigure}[b]{0.22\textwidth}
%        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_o.eps}
%        \caption{Geolife vary $O_r$}
%    \end{subfigure}
%    	 \begin{subfigure}[b]{0.22\textwidth}
%        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_o.eps}
%        \caption{Taxi vary $O_r$}
%    \end{subfigure}
%    \begin{subfigure}[b]{0.22\textwidth}
%	 \includegraphics[width=\textwidth]{/exp/performance/shopping_vary_t.eps}
%        \caption{Shopping vary $T_r$}
%    \end{subfigure}
% 	 \begin{subfigure}[b]{0.22\textwidth}
%        \includegraphics[width=\textwidth]{/exp/performance/geolife_vary_t.eps}
%        \caption{Geolife vary $T_r$}
%    \end{subfigure}
%    	 \begin{subfigure}[b]{0.22\textwidth}
%        \includegraphics[width=\textwidth]{/exp/performance/taxi_vary_t.eps}
%        \caption{Taxi vary $T_r$}
%    \end{subfigure}
% \caption{Scalability of SPARE and TRPM wrt. $O_r$ and $T_r$}
% \label{exp:performance_vary_OT}
%\end{figure}

@@

\begin{figure}[h]
\centering
	  \includegraphics[width=0.35\textwidth]{/exp/spare/detail1.eps}
    \caption{Breakdown of cost of TRPM, SPARE and SPARE-RD.}
    \label{exp:wl}
\end{figure}

\begin{table}[h]
\centering \small
\begin{tabular}{|c|c|c|c|c|}
\hline
\multirow{2}{*}{\textbf{Dataset}} & \multicolumn{2}{c|}{\textbf{SPARE-RD}} & \multicolumn{2}{c|}{\textbf{SPARE}} \\ \cline{2-5} 
                         & Straggler        & Std. Dev.     & Straggler       & Std. Dev.      \\ \hline
Shopping                 & 295              & 41         & 237             & 21       \\ \hline
GeoLife                  & 484              & 108        & 341             & 56       \\ \hline
Taxi                     & 681              & 147        & 580             & 96       \\ \hline
\end{tabular}
  \caption{Statistics of execution time (in seconds) among executors.}
  \label{tbl:strags}
\end{table}

\subsubsection{Load balance}
To study the effect of load balance in the SPARE framework, we use random task allocation (the default setting of Spark) as a baseline, denoted by SPARE-RD, and compare it with our best-fit method. In best-fit, the largest unassigned star is allocated to the currently most lightly loaded reducer.
Figure~\ref{exp:wl} shows the breakdown of the costs in the map-reduce stages for SPARE and SPARE-RD \revised{with TRPM as comparison}. We observe that the map and shuffle time of SPARE and SPARE-RD are identical . The difference is that SPARE incurs an additional overhead to generate an allocation plan for load balance (around $4\%$ of the total cost), resulting in significant savings in the reduce stage (around $20\%$ of the total cost). \revised{We further observe that TRPM takes more time in each phase, which confirms the efficiency of Star Partition and Apriori Enumeration.} We also report the cost of \emph{straggler}, i.e., the longest job, and the standard deviation (Std. Dev.) for all jobs in Table~\ref{tbl:strags}, whose results clearly verify the effectiveness of our allocation strategy for load balance.

\subsubsection{Scalability}
When examining SPARE with increasing computing resources (number of machines), we also compare SPARE with the state-of-the-art solutions for \emph{swarm} and \emph{platoon} in the single-node setting. Since the original \emph{swarm} and \emph{platoon} detectors cannot handle very large-scale datasets, we only use 60\% of each dataset for evaluation. To make fair comparisons, we customize two variants of SPARE to mine \emph{swarm}s and \emph{platoon}s, which are denoted as SPARE-S and SPARE-P respectively. The customization is according to the settings in Table~\ref{tbl:patterns} and the results are reported in Figure~\ref{exp:scalability}. 
First, the centralized schemes are not suitable to discover patterns in 
large-scale trajectory databases. It takes nearly $30$ hours to 
detect \emph{swarm}s and $11$ hours to detect \emph{platoon}s in the Taxi dataset in a single machine. 
In contrast, when utilizing the multi-core \revised{(i.e., single node with 3 executors)} environment, 
SPARE-P achieves $7$ times speedup and SPARE-S achieves $10$ times speedup. 
%our TRPM and SPARE achieves 2.4 times and 7.1 times speedup respectively. 
Second, we see that SPARE schemes demonstrate promising scalability in terms of the number of machines available. The running times decrease almost inversely as more machines are used. 
When all the $11$ nodes ($162$ cores) are available, 
SPARE-P is upto $65$ times and SPARE-S is upto $112$ times better than the state-of-the-art centralized schemes.
%than \emph{platoon} and SPARE-S is upto $112$ times better than \emph{swarm}.
%state-of-the-art \emph{platoon} detector in a centralized server.
